Dataset Summary

### 2018-08-03 Cleaning & subset.Rmd
Separate into functions for easier reuse across different traits

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
```

# Load

```{r cars}
data_raw <- read_csv("data/dr7.0_all_control_data.csv", 
                  col_types = cols(
                      .default = col_character(),
                      project_id = col_character(),
                      id = col_character(),
                      parameter_id = col_character(),
                      age_in_days = col_integer(),
                      date_of_experiment = col_datetime(format = ""),
                      weight = col_double(),
                      phenotyping_center_id = col_character(),
                      production_center_id = col_character(),
                      weight_date = col_datetime(format = ""),
                      date_of_birth = col_datetime(format = ""),
                      procedure_id = col_character(),
                      pipeline_id = col_character(),
                      biological_sample_id = col_character(),
                      biological_model_id = col_character(),
                      weight_days_old = col_integer(),
                      datasource_id = col_character(),
                      experiment_id = col_character(),
                      data_point = col_double(),
                      age_in_weeks = col_integer(),
                      `_version_` = col_character()
                      )
                )
```

# Cleaning:

```{r}
data <- data_raw %>% 
  mutate(parameter_name = tolower(parameter_name) ) %>%
  filter(age_in_days > 0 & age_in_days < 500) %>% 
  select(production_center, project_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
  arrange(production_center, biological_sample_id, age_in_days)
```

# Export

Body size only

```{r}
dir.create("export", F, F)
data %>% filter(parameter_name == "body weight") %>%
  saveRDS("export/body_weight.rds")
```

>>>>

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(metafor)

source("R/meta_analysis.R")
source("R/data_load_clean.R")
source("R/calc_pop_stats.R")
```

# Setup

Load data
```{r cars}
data_raw <- load_raw("data/dr7.0_all_control_data.csv") 
```

Clean data & define population variable
```{r}
data <- clean_raw_data(data_raw) %>%
  mutate(population = sprintf("%s-%s", production_center, strain_name))
```

Export copy of data for body size analysis
```{r}
dir.create("export", F, F)
data %>% filter(parameter_name == "body weight") %>%
  saveRDS("export/body_weight.rds")
```

Create a copy of data for variance analysis

```{r}
data_par_age <- data_subset_parameter_individual_by_age(data, "body weight", age_min = 98, age_center = 100)
```

Now calculate statistics by population:

```{r}
population_stats <- calculate_population_stats(data_par_age)
```

Now analyse by population data:

Sanity checks

```{r}
# i <- seq(1, nrow(population_stats), by = 2)
# all(population_stats$sex[i] == "female")
# all(population_stats$sex[i + 1] == "male")
# all(population_stats$strain_name[i + 1] == population_stats$strain_name[i])
# all(population_stats$production_center[i + 1] == population_stats$production_center[i])
```
Check plot of mean vs variance

```{r}
plot(population_stats$x_bar, population_stats$x_sd, pch=16, log="xy", col = as.factor(population_stats$sex))
```

```{r}
results <- create_meta_analysis_effect_sizes(population_stats)
```

## Compare CVR

```{r}
plot(results$effect_size_CVR, 1/sqrt(results$sample_variance_CVR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.7, 0.7), col=as.factor(results$production_center))
abline(v=0)
```

```{r}
metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
```

## Compare VR

```{r}
plot(results$effect_size_VR, 1/sqrt(results$sample_variance_VR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.8, 0.8), col=as.factor(results$production_center))
abline(v=0)
```

```{r}
metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
```

## Compare Means

```{r}
plot(results$effect_size_RR, 1/sqrt(results$sample_variance_RR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.5, 0.5), col=as.factor(results$production_center))
abline(v=0)
```

```{r}
metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
```
